Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-02 phd/dissertation/chapter3.tex
working on sigma-product

(TODO: Maybe $k+2$ tacts/marks as well, but not as obvious if so.)

(TODO: It's feasible that $k$-limit $\Leftrightarrow$ $1$-limit for
one variation or another.)

@@

\begin{thm}
  $O\not\kmarkwin{k}\clusgame{\oneptcomp\omega_2}{\infty}$.
\end{thm}

@@

\section{TODO: Sigma-products}

\begin{thm}
  Let $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.
  Then $F \codewin PF_{F,C}(\kappa)$.
\end{thm}

@@

\begin{cor}
  $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$
  for all cardinals $\kappa$.
\end{cor}

>>>>

Two types of questions emerge from these results.

\begin{ques}
  Does $\pl O \ktactwin{2} \clusgame{X}{S}$ imply
  $\pl O \ktactwin{2} \congame{X}{S}$? What about for $\kmarkwin{2}$?
\end{ques}

\begin{ques}
  Could $\pl O \ktactwin{k+1} \congame{X}{S}$ actually imply
  $\pl O \tactwin \congame{X}{S}$? What about for $\clusgame{X}{S}$?
\end{ques}

@@

\begin{thm}
  $O\not\kmarkwin{k}\clusgamehard{\oneptcomp\omega_2}{\infty}$.
\end{thm}

@@

\section{Sigma-products}

Knowing the status of $W$-games in simpler spaces yields insight to larger
spaces.

\begin{prop}
  Suppose $S\subseteq Y\subseteq X$, $\limitwin$ is any of $\win$,
  $\ktactwin{k}$, or $\kmarkwin{k}$, and $G(X,S)$ is any of $\congame{X}{S}$,
  $\congamehard{X}{S}$, $\clusgame{X}{S}$, or $\clusgamehard{X}{S}$.

  Then $\pl O \limitwin G(X,S)$ implies $\pl O \limitwin G(Y,S)$.
\end{prop}

\begin{proof}
  Simply intersect the output of the winning strategy in $G(X,S)$ with $Y$.
\end{proof}

A natural superspace of a Fort space is the sigma-product of a discrete
cardinal.

\begin{defn}
  Let $\Sigma_{y} X^\kappa$ be a \term{sigma product} of $X$ with dimension
  $\kappa$ for each $y\in X^\kappa$, the subset of the usual Tychonoff
  product space $X^\kappa$ such that $x\in \Sigma_y X^\kappa$ if and only if
  $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.

  For homogeneous spaces $X$ containing $0$, $y$ is usually assumed to be the
  zero vector $\vec 0$ and the sigma product is written $\Sigma X^\kappa$.
\end{defn}

\begin{prop}
  $\oneptcomp\kappa$ is homeomorphic to the space
  \[
    \{
    x\in \Sigma 2^\kappa
      :
    x(\alpha)=0 \text{ for all but one } \alpha<\kappa
    \}
  \]
\end{prop}

\begin{proof}
  Map $\alpha<\kappa$ to $x_\alpha$ such that
  \[
    x_\alpha(\beta) =
    \left\{
      \begin{array}{ll}
        0 & \beta\not=\alpha \\
        1 & \beta=\alpha
      \end{array}
    \right.
  \]
  and map $\infty$ to the zero vector $\vec0$.
\end{proof}

\begin{cor}
  $\pl O\not\ktactwin{k}\clusgamehard{\SigmaProdR{\omega_1}}{\vec0}$,
  $\pl O\not\kmarkwin{k}\congamehard{\SigmaProdR{\omega_1}}{\vec0}$, and
  $\pl O\not\kmarkwin{k}\clusgamehard{\SigmaProdR{\omega_2}}{\vec0}$.
\end{cor}

While this closes the question on tactics and marks for high dimensional
sigma- (and Tychonoff-) products of the real line, there is another type of
limited information strategy to investigate.

\begin{defn}
  For a game $G=\<M,W\>$ and \term{coding strategy} or \term{code}
  $\sigma:M^2\to M$, the \term{$\sigma$-coding fog-of-war}
  $\gamma_\sigma: M^{<\omega}\to M^{\leq2}$ is the function defined such that
    \[
      \gamma_\sigma(\emptyset) = \emptyset
    \]
  and
    \[
      \gamma_\sigma(s\concat\<x\>) = \<\sigma\circ\gamma_\sigma(s),x\>
    \]

  For a coding strategy $\sigma$, its coresponding strategy is
  $\sigma\circ\gamma_\sigma$. For a game $G$, if $\sigma\circ\gamma_\sigma$
  is a winning strategy for $\pl A$, then $\sigma$ is a winning coding
  strategy and we write $\pl A \codewin G$.
\end{defn}

Intuitively, a $\sigma$-coding fog-of-war converts perfect information of the
game into the last moves of both the player and her opponent, so a player has
a winning coding strategy when she only needs to know the move of her opponent
and her own last move. The term ``coding'' comes from the fact
that a player may encode information about the history of the game into
her own moves, and use this encoded information in later rounds.

Coding strategies have been studied since the earliest days of the
Banach-Mazur game.

\begin{thm}
  (TODO: Cite the precise version of the BM game where a winning strategy
    implies a coding strategy.)
\end{thm}

The hard and normal versions of the $W$ games are all equivalent with regards
to coding strategies since $\pl O$
may always ensure her new move is a subset of her previous move. For
Fort spaces, the question is immediately closed.

\begin{prop}
  $\pl O \codewin \congame{\oneptcomp\kappa}{\infty}$.
\end{prop}

\begin{proof}
  Let $\sigma(\emptyset)=\oneptcomp\kappa$,
  $\sigma(\<U,\alpha\>)=U\setminus\{\alpha\}$ for $\alpha<\kappa$,
  and $\sigma(\<U,\infty\>)=U$. $\pl P$
  cannot legally repeat non-$\infty$ points of the set, so her points converge
  to $\infty$.
\end{proof}

This trick does not simply extend to the $\SigmaProdR\kappa$ case, however.
An open set may only restrict finitely many coordinates of the product,
and a point in $\SigmaProdR\kappa$ may have countably infinite non-zero
coordinates. Thus, information about the previous non-zero coordinates cannot be
directly encoded into the open set.

Circumventing this takes a bit of extra bookkeeping. We proceed by defining
a simpler infinite game for each cardinal $\kappa$.

\begin{game}
  Let $\pfgame\kappa$ denote the \term{point-finite game} with players
  $\pl F$, $\pl C$ for each cardinal $\kappa$.

  In round $n$, $\pl F$ chooses $F_n\in[\kappa]^{<\omega}$, followed by
  $\pl C$ choosing $C_n\in[\kappa\setminus\bigcup_{m\leq n}F_m]^{\leq\omega}$.

  $\pl F$ wins the game if the collection $\{C_n:n<\omega\}$ is a point-finite
  cover of its union $\bigcup_{n<\omega} C_n$, that is, each point in
  $\bigcup_{n<\omega} C_n$ is in $C_n$ only for finitely many $n<\omega$.
\end{game}

\begin{prop}
  $\pl F\win\pfgame\kappa$ for all cardinals $\kappa$.
\end{prop}

\begin{thm}
  $\pl F \codewin \pfgame\kappa$ implies
  $\pl O \codewin \congame{\SigmaProdR\kappa}{\vec0}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a coding strategy for $\pl F$ in $\pfgame\kappa$
  such that $\sigma(F,C)\supset F$.

  For $F\in[\kappa]^{<\omega}$ and $\epsilon>0$ let $U(F,\epsilon)$ be the
  open set in $\mathbb{R}^\kappa$ such that
  \[
    \pi_\alpha(U(F,\epsilon)) =
    \left\{
      \begin{array}{ll}
        (-\epsilon,\epsilon) & \alpha\in F\\
        \mathbb{R} & \alpha\not\in F
      \end{array}
    \right.
  \]
  Note that $F$ is uniquely identifible given
  $U(F,\epsilon)\cap\SigmaProdR\kappa$.

  For each point $x\in\SigmaProdR\kappa$ and $\epsilon\geq 0$, let
  $C_\epsilon(x)\in[\kappa]^{\leq\omega}$
  such that $\alpha\in C_\epsilon(\alpha)$ if and only if
  $|x(\alpha)|\geq\epsilon$.

  TODO: Finish

  % We define the coding strategy $\tau$ for $\pl O$ in
  % $\congame{\SigmaProdR\kappa}{\vec0}$ as follows:
  % \[
  %   \tau(\<U(\tau(\<U,x\>,\epsilon)\cap\SigmaProdR\kappa,x\>)
  %     =
  %   U(\sigma(\<F,C_{2^{-|F|}}(x)\>),2^{-|F|}) \cap \SigmaProdR\kappa
  % \]

  % Assume that $\pl O \not\codewin \congame{\SigmaProdR\kappa}{\vec0}$. Then
  % there exists a legal attack $a=\<a_0,a_1,\dots\>$ by $\pl P$ against $\tau$.
  % Since $a$ does not converge to $\vec0$, it follows there is some
  % $\alpha<\kappa$ such that $a_n(\alpha)$ does not converge to $0$. Thus there
  % is a sequence $n_0<n_1<\dots$ such that $|a_{n_i}(\alpha)|\geq 2^{-n_i}$, and
  % it follows that $\alpha\not\in\sigma(\<F,C_{2^{-|F|}}(x)\>)$ at any stage
  % of the game.

  % Consider the attack $a'=\<$
\end{proof}

TODO:

\begin{thm}
  Let $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.
  Then $\pl F \codewin PF_{F,C}(\kappa)$.
\end{thm}

@@

\begin{cor}
  $O\codewin\congame{\SigmaProdR{\kappa}}{\vec{0}}$
  for all cardinals $\kappa$.
\end{cor}
